Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-06-12 paper/introduction.tex
integrate first batch of Vignesh's comments

where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
into two classes. Continuous parameters, including material thicknesses and
packing fraction, describe the geometry of a given reactor configuration.
\todo{add all the parameters here} Discrete
categorical parameters then specify material selections, including
coolants, armours, and neutron multipliers. We set out to produce a fast TBR
function which takes these same input parameters and approximates the MC TBR
model with the greatest achievable regression performance.

>>>>

where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
into two classes. Continuous parameters, such as material thicknesses and
packing fraction, describe the geometry of a given reactor configuration.
\todo{add all the parameters here} Discrete
categorical parameters then specify material selections, such as
coolants, armours, and neutron multipliers. We set out to produce a fast TBR
function which takes these same input parameters and approximates the MC TBR
model with the greatest achievable regression performance.
